Differential Expression - Dx

### 2020-04-08 cmc-rnaseq-de/Differential-Expression_Dx.Rmd
fix plot facet

# Define biomart object
mart <- biomaRt::useMart(biomart = "ENSEMBL_MART_ENSEMBL",
                host = "uswest.ensembl.org", # Ensembl Release 99 (January 2020)
                dataset = "hsapiens_gene_ensembl")

@@

tmp = DE %>%
  dplyr::filter(adj.P.Val <= 0.05) %>%
  dplyr::select(ensembl_gene_id, Comparison, Tissue) %>%
  group_by(Comparison, Tissue) %>%
  dplyr::summarise(FDR_0_05 = length(unique(ensembl_gene_id)))

tmp1 = DE %>%
  dplyr::filter(adj.P.Val <= 0.05, abs(logFC) >= log2(1.2)) %>%
  dplyr::select(ensembl_gene_id, Comparison, Tissue) %>%
  group_by(Comparison, Tissue) %>%
  dplyr::summarise(FDR_0_05_FC_1.2 = length(unique(ensembl_gene_id)))

@@

p = ggplot(DE, aes(y = -log10(adj.P.Val), x = logFC, color = Direction)) + geom_point() + xlim(c(-1,1))
p = p + scale_color_manual(values = c('green','grey','red')) + theme_bw() %+replace% theme(legend.position = 'top')
p = p + facet_grid(Tissue+.~Comparison, scales = 'fixed')
p
```

>>>>

# Define biomart object
mart <- biomaRt::useMart(biomart = "ENSEMBL_MART_ENSEMBL",
                host = "useast.ensembl.org", # Ensembl Release 99 (January 2020)
                dataset = "hsapiens_gene_ensembl")

@@

tmp = DE %>%
  dplyr::filter(adj.P.Val <= 0.05) %>%
  dplyr::select(ensembl_gene_id, Comparison) %>%
  group_by(Comparison) %>%
  dplyr::summarise(FDR_0_05 = length(unique(ensembl_gene_id)))

tmp1 = DE %>%
  dplyr::filter(adj.P.Val <= 0.05, abs(logFC) >= log2(1.2)) %>%
  dplyr::select(ensembl_gene_id, Comparison) %>%
  group_by(Comparison) %>%
  dplyr::summarise(FDR_0_05_FC_1.2 = length(unique(ensembl_gene_id)))

@@

p = ggplot(DE, aes(y = -log10(adj.P.Val), x = logFC, color = Direction)) + geom_point() + xlim(c(-1,1))
p = p + scale_color_manual(values = c('green','grey','red')) + theme_bw() %+replace% theme(legend.position = 'top')
p = p + facet_grid(~Comparison, scales = 'fixed')
p
```
